---
title: |
  | \LARGE \textbf{\textcolor{usaid_red}{FY`r params$fiscal_yr` EXPENDITURE REPORT}}
  | \LARGE \textbf{\textcolor{usaid_red}{DATA QUALITY REPORT}}
  | \LARGE \textbf{\textcolor{usaid_red}{`r params$ou`}}
output: pdf_document
header-includes: 
  - \usepackage{xcolor}
  - \usepackage{sectsty}
  - \definecolor{usaid_red}{RGB}{186, 12, 47}
  - \definecolor{usaid_blue}{RGB}{0, 47, 108}
  
  - \allsectionsfont{\Large \raggedright \color{usaid_red}}
  
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{graphicx}
  - \usepackage{multirow}
  
  - \usepackage{fancyhdr}
  
  - \pagestyle{fancy}
  - \fancyhead[L,R,C]{}
  - \fancyhead[C]{\bfseries For USAID Internal Use Only}
  
  - \fancypagestyle{plain}{
      \setlength{\headheight}{59pt}
      \fancyhead[R]{\includegraphics[width=5cm]{Horizontal_RGB_294.png}}
      \renewcommand{\headrulewidth}{0pt}}
  
# https://stackoverflow.com/questions/24421235/changing-font-in-pdf-produced-by-rmarkdown
  - \usepackage{helvet}
  - \renewcommand{\familydefault}{\sfdefault}
  
  - \usepackage{titling}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
params:
  ou: "Central Mechanisms"
  fiscal_yr: 2021
  
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

```{r r-setup, include=FALSE}
library(kableExtra)
library(glamr)
library(gophr)
library(glue)
library(tidyverse)
library(formattable)

source('data_quality_source.R')

########  Load Data #####################################
df_fsd <- read_csv("temp/df_fsd.csv")
df_msd <- read_csv("temp/df_msd.csv")
df_hrh <- read_csv("temp/df_hrh.csv")
df_centrals <- read_csv('2021 Central Mechs.csv')


if (params$ou == "Central Mechanisms"){
  fsd_ou <- df_fsd[df_fsd$mech_code %in% df_centrals$`Mechanism ID`,]
  msd_ou <- df_msd[df_msd$mech_code %in% df_centrals$`Mechanism ID`,]
  hrh_ou <- df_hrh[df_hrh$mech_code %in% df_centrals$`Mechanism ID`,]
}else {
  fsd_ou <- df_fsd %>% filter(operatingunit == params$ou)
  msd_ou <- df_msd %>% filter(operatingunit == params$ou) 
  hrh_ou <- df_hrh %>% filter(operating_unit == params$ou)
}

fsd_ou <- fsd_ou %>% mutate(mech_name = lapply(mech_name, abridge, max_len=42))
msd_ou <- msd_ou %>% mutate(mech_name = lapply(mech_name, abridge, max_len=42))
hrh_ou <- hrh_ou %>% mutate(mech_names = lapply(mech_name, abridge, max_len=42))



df_budg_exp<- fsd_ou %>%
  check_budg_exp() %>% 
  ungroup()

df_other <- #df_fsd %>%
  fsd_ou %>%
  percent_other_check() %>% 
  ungroup()

df_pm <- percent_pm_check(fsd_ou) %>%
  ungroup()

df_perc_exp_im <- exp_perc_budg_check_im(fsd_ou) %>%
  ungroup()

df_perc_exp_pa<- exp_perc_budg_check_pa(fsd_ou) %>%
  ungroup()

df_hrh_check <- hrh_check(fsd_ou, hrh_ou)

total_num_mechs <- length(unique(df_fsd$mech_code))
uniq_pe_im <- length(unique(df_perc_exp_im$mech_code))
uniq_pe_pa <- length(unique(df_perc_exp_pa$mech_code))

uniq_budg_exp <- length(unique(df_budg_exp$mech_code))
uniq_other <-length(unique(df_other$mech_code))
uniq_pm <- length(unique(df_pm$mech_code))
uniq_hrh <- length(unique(df_hrh_check$mech_code))

# perc_exp_good <- na.omit(df_perc_exp[df_perc_exp$perc_exp >= 0.9 & df_perc_exp$perc_exp <=1.1, ])
# good_perc_exp <- length(unique(perc_exp_good$mech_code))
```

# \textcolor{usaid_blue}{Care and Treatment (C&T)}
The C&T program area should align with any mechanisms focused on treatment, as well as  linkage to treatment, adherence, and retention services. It is important to review that the below mechanisms have executed their C&T budgets inline with their relevant programmatic (i.e. MER) performance. If a mechanism is overspending their budget with performance that does not match, be prepared to explain why that has occurred.One should review these specific mechanisms to ensure that the spending aligns with their programmatic purpose. 




```{r, echo=FALSE}
col_perc_exp_im <- c("Mechanism Code", "Mechanism Name", 
                  "Total Expenditure", "Total Budgeted", "% Total Expenditures of Budget")

if (uniq_pe_im !=0){
  df_pe_im <- df_perc_exp_im %>%
  mutate(sum_fast = currency(sum_fast)) %>%
  mutate(sum_exp = currency(sum_exp)) %>%
  mutate(perc_exp = percent(perc_exp)) %>%
  mutate(perc_exp = as.character(perc_exp))
df_pe_im$perc_exp[is.na(df_pe_im$perc_exp)] <- '-'

df_pe_im %>%
  kbl(format = "latex", col.names = col_perc_exp_im, longtable=T,
      booktabs = T, escape=T, caption = "Expenditure as Percent of Budget, IM-level") %>%
  kable_paper(latex_options = c("hold_position", "repeat_header"),
              font_size = 9)%>%
  # https://tex.stackexchange.com/questions/98955/auto-resize-tabular-row-height
  row_spec(0, extra_latex_after = "[0.7cm]", bold=TRUE) %>%
  column_spec(1, width = '5em') %>%
  column_spec(2, width = '15em') %>%
  column_spec(3, width = '5em') %>%
  collapse_rows(columns = 1:2, valign="top")
} else{
    data.frame(list("No Mechanisms were flagged")) %>% 
    kbl(format = "latex", col.names = NULL)%>%
    kable_paper(latex_options = c("hold_position"))
}




```
